SpecHunter: Interactively Inferring Taint Specifications Using Bayes Net

### 2021-04-05 My-Papers/SpecHunter/overview.tex
checkpoint

Here, we expound on the core inference algorithm. Inference on the Bayesian
network is divided into two parts: local propagation and global propagation.
Local propagations pass information given by the oracle within a single graph,
whereas global propagations pass the information from one graph to another.

>>>>

Here, we expound on the core inference algorithm. Inference on the Bayesian
network is divided into two parts: local propagation and global propagation.
Local propagations pass information given by the oracle within a single graph,
whereas global propagations pass the information from one graph or several to
another. The Python library \emph{Pomegranate} is used to convert graphs into
Bayesian networks and perform local propagations.   % TODO: cite pomegranate

\paragraph{Local Propagations}

\subparagraph{Picking the Next Node}

We pick the next node based on an algorithm called D-separation

\subparagraph{Overview of the Local Propagation Algorithm}

Local propagations rely on loopy belief propagation algorithm (loopy BP): it is an
approximate version of an exact belief propagation algorithm (sum-product
algorithm), defined on Bayesian networks. Loopy BP may not converge,
nevertheless it provides a nice approximation to the original BP algorithm.
% TODO: cite https://www.jmlr.org/papers/volume6/ihler05a/ihler05a.pdf
Since the algorithm may not converge, we set the maximum number of iterations to
100, the default value set by \emph{Pomegranate}.

% TODO: should we explain a little on loopy BP?

% where should we insert the details of using d-separation?

Figure \emph{xx??} shows our local propagation algorithm. D-separation is used
when we pick the next node to ask of its specification.

% insert algorithm here

\paragraph{Global Propagations}

Global propagations rely on a process which we call ``knowledge transfer''. It
relies on the
